Random Matrix Theory Tools for the Analysis of Functional Magnetic Resonance Imaging Examinations

### 2022-11-08 paper/paper/SPIE/article.tex
[WIP]

\textit{Unfolding Variants}. Following any trimming, the eigenvalues are fit
with a polynomial. The choice of degree has been known to dramatically impact
certain analyses involving the spectral rigidity or level
variance\cite{abul-magdUnfoldingSpectrumChaotic2014,
moralesImprovedUnfoldingDetrending2011, abueleninSpectralUnfoldingChaotic2018,
fossionRandommatrixSpectraTime2013, abueleninEffectUnfoldingSpectral2012}. We
thus compute the rigidity and level variance with all possible combinations of
trimming and unfolding polynomial degree.

@@

When computing the RMT eigenfeatures, the polynomial fitting during unfolding
has a smoothing effect, as do the additional averaging \(\langle\;\rangle_c\)
operations. However, it is possible other, simpler
transformations of the eigenvalues (e.g. uniform or Savitsky-Golay smoothing)
might have equal or greater predictive utility. We thus also test smoothed
variants of the eigenvalues as predictive features: we smooth the sorted
eigenvalues with a uniform (moving average) filter and Savitsky-Golay, using
window sizes of 3, 5, 7, and 9 to yield 8 total "smoothed eigenvalue" features.

>>>>

\textit{Unfolding Variants}. Following any trimming, the eigenvalues are fit
with a polynomial. The choice of degree has been known to dramatically impact
certain analyses involving the spectral rigidity or level
variance\cite{abul-magdUnfoldingSpectrumChaotic2014,
moralesImprovedUnfoldingDetrending2011, abueleninSpectralUnfoldingChaotic2018,
fossionRandommatrixSpectraTime2013, abueleninEffectUnfoldingSpectral2012}. We
thus compute the rigidity and level variance with all possible combinations of
trimming and unfolding polynomial degrees of 3, 5, 7, and 9.

@@

When computing RMT eigenfeatures, the polynomial fitting during unfolding
has a smoothing effect, as do the additional averaging \(\langle\;\rangle_c\)
operations. However, it is possible other, simpler
transformations of the eigenvalues (e.g. uniform or Savitsky-Golay smoothing)
might have equal or greater predictive utility. We thus also test smoothed
variants of the eigenvalues as predictive features: we smooth the sorted
eigenvalues with a uniform (moving average) filter and Savitsky-Golay, using
window sizes of 3, 5, 7, and 9 to yield 8 total ``smoothed eigenvalue'' features.
